Online Multiclass Linear Classification with Bandit Feedback

### 2019-01-15 ICML-submission/from-weak-separability-to-strong-separability.tex
Fixes

In this section, we focus on the setting of online bandit multiclass
linear prediction, where the set of examples shown by the adversary is weakly
linearly separable (Definition~\ref{definition:weak-linear-separability}).
Throughout this section, we assume without loss of generality that
all examples lie in $\B(0,1)$, the unit $\ell_2$ ball of
$\R^d$.\footnote{Consider the following preprocessing step: upon seeing every
example $x_t$, we define $\hat{x}_t = \frac{x_t}{\|x_t\|}$ as its $\ell_2$ normalization.
It can be easily checked that if $(x_1,y_1), \ldots, (x_T,y_T)$ is weakly linearly
separable by margin $\gamma$ and all $\| x_t \|$'s' have norm at most $R$, then the set of
normalized examples $(\hat{x}_1,y_1), \ldots, (\hat{x}_T,y_T)$ is weakly linearly
separable by margin $\gamma/R$.}
Note that Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
alone does not guarantee a finite mistake bound in this setting, as weak linear separability
does not imply strong linear separability.

%from the unit ball of
%$\R^d$ into a infinite-dimensional inner product space that

In this section, we consider a kernel function $k(\cdot, \cdot)$
whose corresponding feature map $\phi(\cdot)$ can transform a set of
\emph{weakly} linear separable examples to \emph{strongly} separable.
Specifically, $\phi$
has the property
that if a set of labeled examples in the unit ball is weakly linearly
separable with a margin $\gamma$, then after applying $\phi$ the examples
become strongly linearly separable with a margin $\gamma'$ and their
norms are bounded by $2$. The parameter $\gamma'$ is a function of the old
margin $\gamma$ and the number of classes $K$, and is specified in
\autoref{theorem:margin-transformation} below.

Specifically, the kernel function $k: \B(0,1) \times \B(0,1) \to \R$ is defined as:
$$
k(x,x') = \frac{1}{1 - \frac{1}{2}\ip{x}{x'}_{\R^d}} \; ,
$$
We note that the formula for $k$ implies that $k(x,x) < +\infty$ for any $x$ in
$\B(0,1)$. We also note
that kernel function $k(x,x')$ can be evaluated in $O(d)$ time.

Consider the
classical real separable Hilbert space $\ell_2 = \{ x \in \R^\infty ~:~
\sum_{i=1}^\infty x_i^2 < + \infty \}$ equipped with the standard inner product
$\ip{x}{x'}_{\ell_2} = \sum_{i=1}^\infty x_i x'_i$.
Through indexing the coordinates of
$\ell_2$ by $d$-tuples $(\alpha_1, \alpha_2, \dots, \alpha_d)$ of non-negative
integers, the feature map that corresponds to $k$, $\phi: \B(0,1) \to \ell_2$, is defined as follows:
\begin{align}
& \left(\phi(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)} = x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d} \nonumber \\
& \qquad \cdot \sqrt{2^{-(\alpha_1 + \alpha_2 + \dots + \alpha_d)} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}}
\label{eqn:phi}
\end{align}
where $\binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d} = \frac{(\alpha_1 + \alpha_2 + \dots + \alpha_d)!}{\alpha_1! \alpha_2! \dots \alpha_d!}$
is the multinomial coefficient.
It can be easily checked that
\[ k(x,x') = \ip{\phi(x)}{\phi(x')}_{\ell_2}. \]

%The mapping is defined by
%and therefore $\phi(x)$ lies in $\ell_2$.
%The domain of $\phi$ is the unit ball of $\R^d$. The co-domain of $\phi$ is

The following theorem is our main technical result in this section; we defer its
proof to Section~\ref{sec:margin-trans}.

\begin{theorem}[Margin transformation]
\label{theorem:margin-transformation}
Let $(x_1, y_1)$, $(x_2, y_2)$, $\dots$, $(x_T, y_T)$ in $\R^d \times \{1,2,\dots,K\}$
be a set of labeled examples that is weakly linearly separable with margin $\gamma > 0$.
In addition, for all $t$ in $\cbr{1,\ldots,T}$, $\norm{x_t} \le 1$.
Let $\phi$ be as defined in Equation~\eqref{eqn:phi}, and
\begin{align*}
r & = 2 \left\lceil \frac{1}{4} \log_2(4K-3) \right\rceil + 1, \quad \quad s = \left \lceil \log_2(2/\gamma) \right \rceil, \\
\gamma_1 & = \frac{1}{2\sqrt{K}}  \\
& \ \cdot \left(376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{-\frac{1}{2} \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}, \\
\gamma_2 & = \frac{2^{s(s+1)r(K-1)} }{4\sqrt{K}(2K-5/2) 2^{K-1}} \\
& \ \cdot \left(2^{2s+1} r(K-1) (4s+2)^2 \right)^{-(s+1/2)r(K-1)} \; .
\end{align*}
Then, the set of labeled examples transformed by $\phi$,
namely $(\phi(x_1), y_1), (\phi(x_2), y_2), \dots,
(\phi(x_T), y_T)$, is strongly linearly separable with margin $\gamma' =
\max\{\gamma_1, \gamma_2\}$. In addition, $\norm{\phi(x_1)}_{\ell_2},
\norm{\phi(x_2)}_{\ell_2}, \dots, \norm{\phi(x_T)}_{\ell_2} \le 2$.
\end{theorem}

We are now ready to derive a mistake bound for Algorithm~\ref{algorithm:kernelized} with kernel
function $k(x,x') = \ip{\phi(x)}{\phi(x')}_{\ell_2}$. This is done by simply invoking
\autoref{theorem:kernelized-upper-bound} with the
modified margin $\gamma'$ from \autoref{theorem:margin-transformation}.
The mistake bound is stated as \autoref{corollary:weakly-separable-examples-mistake-upper-bound}.

%As a corollary of \autoref{theorem:margin-transformation} and
%\autoref{theorem:strongly-separable-examples-mistake-upper-bound}
%we get the mistake bound for Algorithm~\ref{algorithm:kernelized}
%under the weak separability condition.

\begin{corollary}[Mistake upper bound]
\label{corollary:weakly-separable-examples-mistake-upper-bound}
Let $K$ be a positive
integer, $\gamma$ be a positive real number, $R$ be a non-negative real number. If
$L = ((x_1, y_1), (x_2, y_2), \dots, (x_T, y_T))$ is a sequence of labeled examples in
$V \times \{1,2,\dots,K\}$ such that
\begin{enumerate}
  \item $L$ is weakly linearly separable with margin $\gamma$,
  \item for all $t$ in $\cbr{1,2,\ldots,T}$, $\norm{x_t} \le 1$,
\end{enumerate}
then the expected number of mistakes
Algorithm~\ref{algorithm:kernelized}
makes is at most $2^{\widetilde{O}(\min(K \log^2
\frac{1}{\gamma}, \sqrt{\frac{1}{\gamma}} \log K))}$.
\end{corollary}
%, \norm{x_2}, \dots, \norm{x_T}
% (Definition~\ref{definition:weak-linear-separability})

\subsection{Proof of Theorem~\ref{theorem:margin-transformation}}
\label{sec:margin-trans}
The idea behind construction and analysis of the mapping $\phi$ is polynomial
approximation. According to the well known Stone-Weierstrass theorem (see
e.g.~\citet[Section~10.10]{Davidson-Donsig-2010}), on a compact set,
multivariate polynomials uniformly approximate any continuous function.
Intuitively speaking, we use a multivariate polynomial to approximate, on the
unit ball of $\R^d$, the indicator function corresponding to the intersection of
$m=K-1$ halfspaces. Within margin $\gamma$ along the decision boundary, we allow
the polynomial to attain arbitrary value. The polynomial separates examples in
one class from examples in the other classes. To be able to quantify $\gamma'$
we need to quantify certain parameters of the approximating polynomial. We
construct two different polynomials with different parameters. The parameters
are quantified in
Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
stated below.

>>>>

In this section, we case when the sequence of examples shown by the adversary is
weakly linearly separable
(Definition~\ref{definition:weak-linear-separability}). Throughout this section,
we assume without loss of generality that all examples lie in the unit ball
$\B(0,1) \subseteq \R^d$.\footnote{Consider the following preprocessing step:
upon seeing every example $x_t$, we define $\hat{x}_t = \frac{x_t}{\norm{x_t}}$
as its normalization. It can be easily checked that if $(x_1,y_1), \dots,
(x_T,y_T)$ is weakly linearly separable by margin $\gamma$ and $\norm{x_t} \le
\R$ for all $t$, then the set of normalized examples $(\hat{x}_1,y_1), \dots,
(\hat{x}_T,y_T)$ is weakly linearly separable by margin $\gamma/R$.} Note that
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
alone does not guarantee a finite mistake bound in this setting, as weak linear
separability does not imply strong linear separability.

We consider a kernel function $k(\cdot, \cdot)$ whose corresponding feature map
$\phi(\cdot)$ transforms any sequence of \emph{weakly} linearly separable
examples to \emph{strongly} linearly separable sequence of examples.
Specifically, $\phi$ has the property that if a set of labeled examples in
$B(0,1)$ is weakly linearly separable with a margin $\gamma$, then after
applying $\phi$ the examples become strongly linearly separable with a margin
$\gamma'$ and their norms are bounded by $2$. The parameter $\gamma'$ is a
function of the old margin $\gamma$ and the number of classes $K$, and is
specified in \autoref{theorem:margin-transformation} below.

The kernel function $k:\B(0,1) \times \B(0,1) \to \R$ is defined as
$$
k(x,x') = \frac{1}{1 - \frac{1}{2}\ip{x}{x'}_{\R^d}} \; .
$$
Note that kernel function $k(x,x')$ can be evaluated in $O(d)$ time.

Consider the classical real separable Hilbert space $\ell_2 = \{ x \in \R^\infty
~:~ \sum_{i=1}^\infty x_i^2 < + \infty \}$ equipped with the standard inner
product $\ip{x}{x'}_{\ell_2} = \sum_{i=1}^\infty x_i x'_i$. If we index the
coordinates of $\ell_2$ by $d$-tuples $(\alpha_1, \alpha_2, \dots, \alpha_d)$ of
non-negative integers, the feature map that corresponds to $k$ is $\phi: \B(0,1)
\to \ell_2$,
\begin{align}
& \left(\phi(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)} = x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d} \nonumber \\
& \qquad \cdot \sqrt{2^{-(\alpha_1 + \alpha_2 + \dots + \alpha_d)} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}}
\label{equation:phi}
\end{align}
where $\binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots,
\alpha_d} = \frac{(\alpha_1 + \alpha_2 + \dots + \alpha_d)!}{\alpha_1! \alpha_2!
\dots \alpha_d!}$ is the multinomial coefficient. It can be easily checked that
$$
k(x,x') = \ip{\phi(x)}{\phi(x')}_{\ell_2}.
$$
The last equality together with the formula for $k$ implies that $k(x,x) <
+\infty$ for any $x$ in $\B(0,1)$.

The following theorem is our main technical result in this section. We defer its
proof to Section~\ref{section:margin-transformation}.

\begin{theorem}[Margin transformation]
\label{theorem:margin-transformation}
Let $(x_1, y_1)$, $(x_2, y_2)$, $\dots$, $(x_T, y_T)$ in $\B(0,1) \times
\{1,2,\dots,K\}$ be a sequence of labeled examples that is weakly linearly
separable with margin $\gamma > 0$. Let $\phi$ be as defined in
Equation~\eqref{equation:phi}, and
\begingroup
\allowdisplaybreaks
\begin{align*}
r & = 2 \left\lceil \frac{1}{4} \log_2(4K-3) \right\rceil + 1, \quad \quad s = \left \lceil \log_2(2/\gamma) \right \rceil, \\
\gamma_1 & = \frac{1}{2\sqrt{K}}  \\
& \ \cdot \left(376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{-\frac{1}{2} \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}, \\
\gamma_2 & = \frac{2^{s(s+1)r(K-1)} }{4\sqrt{K}(2K-5/2) 2^{K-1}} \\
& \ \cdot \left(2^{2s+1} r(K-1) (4s+2)^2 \right)^{-(s+1/2)r(K-1)} \; .
\end{align*}
\endgroup
Then, the set of labeled examples transformed by $\phi$,
namely $(\phi(x_1), y_1), (\phi(x_2), y_2), \dots,
(\phi(x_T), y_T)$, is strongly linearly separable with margin $\gamma' =
\max\{\gamma_1, \gamma_2\}$. In addition, $\norm{\phi(x_1)}_{\ell_2},
\norm{\phi(x_2)}_{\ell_2}, \dots, \norm{\phi(x_T)}_{\ell_2} \le 2$.
\end{theorem}

Using this theorem we derive a mistake bound for
Algorithm~\ref{algorithm:kernelized} with kernel function $k(x,x') =
\ip{\phi(x)}{\phi(x')}_{\ell_2}$. This is done by simply invoking
\autoref{theorem:kernelized-upper-bound} with the modified margin $\gamma'$ from
\autoref{theorem:margin-transformation}. The mistake bound is stated as
\autoref{corollary:weakly-separable-examples-mistake-upper-bound} below.

\begin{corollary}[Mistake upper bound]
\label{corollary:weakly-separable-examples-mistake-upper-bound}
Let $K$ be a positive integer and let $\gamma$ be a positive real number. If $L
= ((x_1, y_1), (x_2, y_2), \dots, (x_T, y_T))$ is a sequence of labeled examples
in $V \times \{1,2,\dots,K\}$ such that
\begin{enumerate}
\item $L$ is weakly linearly separable with margin $\gamma$,
\item for all $t$ in $\cbr{1,2,\dots,T}$, $\norm{x_t} \le 1$,
\end{enumerate}
then the expected number of mistakes Algorithm~\ref{algorithm:kernelized} makes
is at most $2^{\widetilde{O}(\min(K \log^2 \frac{1}{\gamma},
\sqrt{\frac{1}{\gamma}} \log K))}$.
\end{corollary}

\subsection{Proof of Theorem~\ref{theorem:margin-transformation}}
\label{section:margin-transformation}

\paragraph{Overview.} The idea behind construction and analysis of the mapping
$\phi$ is polynomial approximation. Specifically, we give $k$ polynomials $p_1$,
$\ldots$, $p_k$, such that:
\begin{align}
\label{equation:poly-pos}
& \forall t \in \cbr{1,2,\dots,T}, p_{y_t}(x_t) \ge \frac{\gamma'}2 \; ,
\\
\label{equation:poly-neg}
& \begin{gathered}
\forall t \in \cbr{1,2,\dots,T} \ \forall i \in \cbr{1,2,\ldots,K} \setminus \cbr{y_t} \\
p_i(x_t) \leq -\frac{\gamma'}2 \; .
\end{gathered}
\end{align}
As each polynomial $p_i$ can be written as $\ip{c_i}{\phi(x)}$ for some $c_i \in
\ell_2$, it immediately shows that the set of examples $(\phi(x_1),y_1), \ldots,
(\phi(x_T),y_T)$ is strongly linear separable.

To construct $p_1, p_2, \dots, p_k$ that satisfy
Equations~\eqref{equation:poly-pos} and~\eqref{equation:poly-neg}, we consider
constructing each $p_i$ separately. Specifically, $p_i$ needs to satisfy that:
\begin{align}
\label{equation:poly-pos-i}
\forall t \in \cbr{1,2,\dots,T}, y_t = i \Rightarrow p_i(y_t) \ge \frac{\gamma'}2 \; , \\
\label{equation:poly-neg-i}
\forall t \in \cbr{1,2,\dots,T}, y_t \neq i \Rightarrow p_i(y_t) \le -\frac{\gamma'}2 \; .
\end{align}

Under the weak linear separability assumption, we note that all examples from
class $i$ lie in
\[ R_i^+ = \bigcap_{j \in \cbr{1,\ldots,K} \setminus \cbr{i}} \cbr{x: \ip{w_i - w_j}{x} \geq \gamma}, \] and all examples from the remaining classes lie in
\[ R_i^- = \bigcup_{j \in \cbr{1,\ldots,K} \setminus \cbr{i}} \cbr{x: \ip{w_i - w_j}{x} \leq  -\gamma}. \]
Therefore, to satisfy Equations~\eqref{equation:poly-pos-i}
and~\eqref{equation:poly-neg-i}, it suffices to construct $p_i$ such that:
\begin{align*}
x \in R_i^+ & \Rightarrow p_i(x) \ge \frac {\gamma'} 2 \\
x \in R_i^- & \Rightarrow p_i(x) \le - \frac {\gamma'} 2
\end{align*}

According to the well known Stone-Weierstrass theorem (see
e.g.~\citet[Section~10.10]{Davidson-Donsig-2010}), on a compact set,
multivariate polynomials uniformly approximate any continuous function.
Intuitively speaking, we use a multivariate polynomial to approximate, on the
unit ball of $\R^d$, the indicator function corresponding to the intersection of
$m=K-1$ halfspaces. Within margin $\gamma$ along the decision boundary, we allow
the polynomial to attain arbitrary value. The polynomial separates examples in
one class from examples in the other classes. To be able to quantify $\gamma'$
we need to quantify certain parameters of the approximating polynomial. We
construct two different polynomials with different parameters. The parameters
are quantified in
Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
stated below.

### 2019-01-15 ICML-submission/introduction.tex
Fixes

The performance of the learner is measured by its cumulative number of
mistakes $\sum_{t=1}^T z_t = \sum_{t=1}^T \indicator{\widehat y_t \neq y_t}$.
The bandit feedback is a natural feedback model motivated by applications
including online advertising and online content optimization.
\chicheng{Perhaps cite~\cite{Kakade-Shalev-Shwartz-Tewari-2008}?}

@@

In the full-information feedback setting, it is well known that if all examples
have norm at most $R$ and are weakly linearly separable with a margin $\gamma$,
then the \textsc{Multiclass Perceptron} algorithm makes at most $\lfloor
2(R/\gamma)^2 \rfloor$ mistakes.
The guarantees provided by \textsc{Multiclass Perceptron} is very satisfying,
since it achieves an information-theoretically optimal mistake upper bound,
while having low time and memory complexities.
\footnote{These results are standard in the literature. For completeness, we present Theorems~\ref{theorem:mutliclass-perceptron-mistake-upper-bound}
and~\ref{theorem:online-multiclass-classification-mistake-lower-bound},
along with their proofs in Appendix~\ref{section:multiclass-perceptron-proofs}.}
%the \textsc{Multiclass Perceptron} algorithm

The bandit feedback setting, however, is much more challenging. For the case
when the examples are strongly linearly separable, to the best
of our knowledge, it is not known how to design
an efficient algorithm with a finite mistake bound before our work.
\footnote{Although~\cite{Chen-Chen-Zhang-Chen-Zhang-2009} claimed that their
Conservative OVA algorithm with PA-I update has a finite mistake bound under the
strong linear separability condition, their proof of Theorem 2 is incorrect.
Their Lemma 4 cannot be directly applied to the bandit setting, as the algorithm
only makes updates on a subset of the $w_i$'s.}
We design a simple and
efficient algorithm, namely
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples},
that has an expected number of mistakes at most $(K-1) \lfloor
4(R/\gamma)^2 \rfloor$. The algorithm can be viewed as running $K$ copies of the
\textsc{Binary Perceptron} algorithm, one copy for each class. Intuitively
speaking, the factor $K-1$ is the price we pay for the bandit feedback, or more
precisely, the lack of full-information feedback. We also prove that any
(possibly randomized) algorithm makes $\Omega(K (R/\gamma)^2))$ mistakes in the
worst case.

For the case when examples are weakly linearly separable,
we construct a feature
mapping $\phi$ that makes them \emph{strongly} linearly separable. We then
use the kernelized version of the algorithm, namely Algorithm~\ref{algorithm:kernelized},
 for the strongly separable case; for
 more details on kernel methods see e.g.~\citet{Scholkopf-Smola-2002} and
\citet{Shawe-Taylor-Cristianini-2004}. The kernel $k(x,y)$ corresponding to the
feature mapping $\phi$ has a simple explicit formula and can be computed in
$O(d)$ time.

The number of mistakes of the kernelized algorithm depends on the margin in the
corresponding feature space. We analyze how the margin parameter of weak
separability in the original space $\R^d$ gets transformed into a margin
parameter of strong separability in the new feature space. This problem is
related to the problem of learning intersection of halfspaces and has been
studied previously by \citet{Klivans-Servedio-2008}.
As a side result, we improve on the results of
\citet{Klivans-Servedio-2008} by removing the dependency of the margin parameter
 on the original dimension $d$.
%inspired by~\cite{Klivans-Servedio-2008},
%In fact, our analysis can
%be viewed as a follow up on their work.

>>>>

The performance of the learner is measured by its cumulative number of
mistakes $\sum_{t=1}^T z_t = \sum_{t=1}^T \indicator{\widehat y_t \neq y_t}$.

@@

In the full-information feedback setting, it is well known that if all examples
have norm at most $R$ and are weakly linearly separable with a margin $\gamma$,
then the \textsc{Multiclass Perceptron} algorithm makes at most $\lfloor
2(R/\gamma)^2 \rfloor$ mistakes. The guarantees provided by \textsc{Multiclass
Perceptron} is very satisfying, since it achieves an information-theoretically
optimal mistake upper bound, while having low time and memory complexities.
\footnote{These results are standard in the literature. For completeness, we
present Theorems~\ref{theorem:mutliclass-perceptron-mistake-upper-bound}
and~\ref{theorem:online-multiclass-classification-mistake-lower-bound}, along
with their proofs in Appendix~\ref{section:multiclass-perceptron-proofs}.}

The bandit feedback setting, however, is much more challenging. For the case
when the examples are strongly linearly separable, to the best of our knowledge,
it is not known how to design an efficient algorithm with a finite mistake bound
before our work. \footnote{Although~\cite{Chen-Chen-Zhang-Chen-Zhang-2009}
claimed that their Conservative OVA algorithm with PA-I update has a finite
mistake bound under the strong linear separability condition, their proof of
Theorem 2 is incorrect. Their Lemma 4 cannot be directly applied to the bandit
setting, as the algorithm only makes updates on a subset of the $w_i$'s.} We
design a simple and efficient algorithm, namely
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples},
that has an expected number of mistakes at most $(K-1) \lfloor 4(R/\gamma)^2
\rfloor$. The algorithm can be viewed as running $K$ copies of the
\textsc{Binary Perceptron} algorithm, one copy for each class. Intuitively
speaking, the $O(K)$ multiplicative factor is the price we pay for the bandit
feedback, or more precisely, the lack of full-information feedback. We also
prove that any (possibly randomized) algorithm makes $\Omega(K (R/\gamma)^2))$
mistakes in the worst case.

For the case when examples are weakly linearly separable, we construct a feature
mapping $\phi$ that makes them \emph{strongly} linearly separable. We then use
the kernelized version of the algorithm, namely
Algorithm~\ref{algorithm:kernelized}, for the strongly separable case; for more
details on kernel methods see e.g.~\citet{Scholkopf-Smola-2002} and
\citet{Shawe-Taylor-Cristianini-2004}. The kernel $k(x,x')$ corresponding to the
feature mapping $\phi$ has a simple explicit formula and can be computed in
$O(d)$ time.

The number of mistakes of the kernelized algorithm depends on the margin in the
corresponding feature space. We analyze how the margin parameter of weak
separability in the original space $\R^d$ gets transformed into a margin
parameter of strong separability in the new feature space. This problem is
related to the problem of learning intersection of halfspaces and has been
studied previously by \citet{Klivans-Servedio-2008}. As a side result, we
improve on the results of \citet{Klivans-Servedio-2008} by removing the
dependency on the original dimension $d$.
